Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-19 paper/ijcai/paper.tex
intro

This paper reports the results of a comprehensive study evaluating the impact of
combining \ds{} and \sfl{} to improve software fault localization, a technique
we coin as \comb{}. The intuition for the combination is that several highly
ranked statements, albeit covered by failing executions, may be unrelated to the
fault. Our empirical study involves \numFaults{} faults from \numPrograms{}
different programs comprised in the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to evaluate
fault localization research. Prior work reported promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation or used
archaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

@@

>>>>

This paper reports the results of a a study using real-world applications to
evaluate the impact of combining \ds{} and \sfl{} to improve software fault
localization. We coin the toolset materializing this approach as \comb{}.  The
intuition for the combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Our empirical
study involves \numFaults{} faults from \numPrograms{} different programs
comprised in the Defects4J (D4J) dataset~\cite{just-defects4j-issta2014}, which
is frequently used to evaluate fault localization research. Prior work reported
promising results in this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair},
but they used a non-representative set of subjects in their evaluation or used
archaic methods to evaluate technique
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

@@

The tool as well as a replication package will be available once double-blind
requirements are lifted.
